\vskip-0.6in Temporary Trade Barriers: When Will They End?

### 2017-10-19 draft.tex
fix typos in proof of \pi results

The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to a positive shift in the $\pi(\cdot)$ function; to show that the renewal probability is increasing in such a positive shift, I must demonstrate that the following derivative is negative: 
\begin{equation}
  \frac{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + Z(\bta,\tad) \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right)}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
  \label{appex:pi}
\end{equation}

This can be simplied to
\[
  \frac{\left(\mathit{CS}_X(\tad) + \mathit{TR}(\tad)  -\mathit{CS}_X(\tau^a) - \mathit{TR}(\tau^a) \right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) }{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
\]

@@

We can rewrite $\frac{\partial r(e,\bta,\tad)}{\partial \pi(\cdot)} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial \pi(\cdot)} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial Z(\bta,\tad)} \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} = - f_\ga \frac{\partial Z(\bta,\tad)}{\partial \tau^a}$, where $F_\ga (Z(\bta,\tad))$ is the CDF of $\ga$ and $f_\ga (Z(\bta,\tad))$ is the pdf of $\ga$ and $Z(\bta,\tad)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.

Then $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)} = - \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \pi(\cdot)} \right) = 
	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \pi(\cdot) \partial e} - \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} \frac{\partial f_\ga}{\partial e} $
where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$. $-\frac{\partial Z(\bta,\tad)}{\partial \pi(
cdot)} = - \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) \leq 0$ by assumption, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)} \leq 0$. Thus the sign of $\frac{\partial e}{\partial \pi(\cdot)}$ is ambiguous.  $\hfill\blacksquare$

>>>>

The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to a positive shift in the $\pi(\cdot)$ function; to show that the renewal probability is increasing in such a positive shift, I must demonstrate that the following derivative is negative: 
\[
  \frac{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + Z(\bta,\tad) \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right)}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
\]

This can be simplied to
\begin{equation}
  \frac{\left(\mathit{CS}_X(\tad) + \mathit{TR}(\tad)  -\mathit{CS}_X(\tau^a) - \mathit{TR}(\tau^a) \right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) }{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
\label{appex:pi}
\end{equation}

@@

We can rewrite $\frac{\partial r(e,\bta,\tad)}{\partial \pi(\cdot)} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial \pi(\cdot)} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial Z(\bta,\tad)} \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} = - f_\ga \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)}$, where $F_\ga (Z(\bta,\tad))$ is the CDF of $\ga$ and $f_\ga (Z(\bta,\tad))$ is the pdf of $\ga$ and $Z(\bta,\tad)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.

Then $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)} = - \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \pi(\cdot)} \right) = 
	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \pi(\cdot) \partial e} - \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} \frac{\partial f_\ga}{\partial e} $
where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$. $-\frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} = - \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) \leq 0$ by assumption, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)} \leq 0$. Thus the sign of $\frac{\partial e}{\partial \pi(\cdot)}$ is ambiguous.  $\hfill\blacksquare$
